---
title: "p8105_hw1_jw3726"
author: "Jiabei Wang"
date: "2018年9月13日"
output: github_document

#```
#punif(10, min=0, max=5, lower.tail= TRUE, log.p= FALSE)
#```
```{r}
#create a data frame comprised of a random sample of size 10 from a uniform[0, 5] distribution
library(tidyverse)
example_df = tibble(
sample=runif(10, min=0, max=5),
#A logical vector indicating whether elements of the sample are greater than 2
logical = sample > 2,
#A (length-10) character vector
vec_char = c("My", "name", "is", "Jiabei", "and", "I", "am", "a", "graduate", "student"), 
#A (length-10) factor vector
vec_factor = factor(c("male", "male", "male", "male", "male", "female", "female", "female", "female", "female")))
mean(example_df$sample)
mean(example_df$logical)
mean(example_df$vec_char)
mean(example_df$vec_factor)
as.numeric(example_df$logical)
as.numeric(example_df$vec_char)
as.numeric(example_df$vec_factor)
as.numeric(as.factor(example_df$vec_char))
as.numeric(as.character(example_df$vec_factor))




```
to calculate the mean, variable "sample" and "logical" work, since they are numeric. Varible "vec_char" and "vec_factor" don't work, since they are not numeric. 
when use "as. numeric"to logical, vec_char, and vec_factor, logical and vec_factor are converted to numeric numbers, while vec_char cannot be converted. 

```{r}
#Create a data frame 
library(tidyverse)
#x: a random sample of size 1000 from a standard Normal distribution
example_df = tibble(
x = rnorm(1000, mean = 0, sd = 1),
#y: a random sample of size 1000 from a standard Normal distribution
y = rnorm(1000, mean = 0, sd = 1),
#A logical vector indicating whether the x + y > 0
logical = x + y > 0, 
#A numeric vector created by coercing the above logical vector
numeric_vector = as.numeric(logical), 
#A factor vector created by coercing the above logical vector
factor_vector = as.factor(logical)) 
mean(example_df$x)
median(example_df$x)





```
#short description using inline R code
The size of dataset is `r dim(example_df)` 
The mean is `r mean(example_df$x)`
The median is `r median(example_df$x)`
The  proportion of cases for which the logical vector is TRUE is `r mean(example_df$logical)`

```{r}
#Make a scatterplot of y vs x, and color points using the logical variable 
ggplot(example_df, aes(x = x, y = y, color = logical)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
#numeric variable
ggplot(example_df, aes(x = x, y = y, color = numeric_vector)) + geom_point()
#factor variable
ggplot(example_df, aes(x = x, y = y, color = factor_vector)) + geom_point()
```
The three color spots look similar, and they are intensive around x=0 and y=0. It seems like the plots all have positive relationship.








